Distributions

### 2021-12-13 Ch2_distributions/Ch2_Figures.Rmd
small preview of figures

>>>>

# Fits

```{r}
load("Ch2_distributions/fits_df.RData")
```

```{r}
nboots <- 1000

cp.fits %>%
  dplyr::select(., bic, dist, dBIC, boot) %>%
  group_by(boot) %>%
  distinct() %>%
  ungroup() %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  mutate(model = "CP") %>%
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  geom_col()

pp.fits %>%
  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
  group_by(fgroup, boot) %>%
  distinct() %>%
  group_by(fgroup) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
  geom_col()

np.fits %>%
  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
  group_by(individual, boot) %>%
  distinct() %>%
  group_by(individual) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
  geom_col()
